Semilattice Graphs for Distributed Databases

### 2022-10-04 paper/paper.tex
latresult
semiL

      The total space $\mathrm{SemiTot}(L, g)$ is a preorder whose elements consist of pairs $(x, x')$ where $x : L$ and $x' : g(x)$. We consider $(x, x') \leq (y, y')$ when $x \leq y$ and $g(x \leq y)(x') \leq y'$. Consider two elements of the total space, $(x, x'), (y, y')$. Their join is defined as $$(x, x') \vee (y, y') := (x \vee y', g(x \leq x \vee y)(x') \vee g(y \leq x \vee y)(y'))$$.

      \begin{theorem}
        The total space $\mathrm{SemiTot}(L, g)$ of a semilattice $L$ and a semilattice fibration $g$ is a semilattice.
      \end{theorem}
      \begin{proof}
        We must show that this join is commutative, associative, and idempotent.
        \begin{itemize}
          \item \emph{Commutative}:
            \begin{align*}
              (x, x') \vee (y, y') &= \left(x \vee y, g(x \leq x \vee y)(x') \vee g(y \leq x \vee y)(y')\right) \\
              &= \left(y \vee x, g(y \leq y \vee x)(y') \vee g(x \leq y \vee x)(x')\right) \\
              &= (y, y') \vee (x, x')
            \end{align*}
          \item \emph{Associative}:
            \begin{align*} &((x, x') \vee (y, y')) \vee (z, z')  \\
              =& \left(x \vee y \vee z, g(x \vee y \leq x \vee y \vee z)(g(x \leq x \vee y)(x') \vee g(y \leq x \vee y)(y')) \vee g(z \leq x \vee y \vee z)(z')\right) \\
              =& \left(x \vee y \vee z, g(x \leq x \vee y \vee z)(x') \vee g(y \leq x \vee y \vee z)(y') \vee g(z \leq x \vee y \vee z)(z')\right) \\
              =& \left(x \vee y \vee z, g(x \leq x \vee y \vee z)(x') \vee g(y \vee z \leq x \vee y \vee z)(g(y \leq y \vee z)(y') \vee g(z \leq y \vee z)(z'))\right) \\
              =& (x, x') \vee ((y, y') \vee (z, z'))
            \end{align*}
          \item \emph{Idempotent}: 
            \begin{align*}
              (x, x') \vee (x, x') &= \left(x \vee x, g(x \leq x \vee x)(x') \vee g(x \leq x \vee x)(x')\right) \\
              &= \left(x, g(x \leq x)(x')\right) \\
              &= (x, x')
            \end{align*}
        \end{itemize}
      \end{proof}

@@

      We write $\mathrm{SemiFibration}(L)$ for the set of semilattice fibrations on $L$.

@@

      The total space $\mathrm{SemiTot}(L, l, t)$ is then a semilattice whose elements are pairs $(x, x')$ where $x : L$ and $x' : l(x)$. The join is defined as $(x, x') \vee (y, y') := (x \vee y, t(x, x \vee y)(x') \vee t(y, x \vee y)(y'))$. This is equivalent to the above category-theoretic definition, proving it is a semilattice.

@@

      \begin{align*}
        L_0 &: \mathrm{Semilattice} & \\
        (l_n, t_n) &: \mathrm{SemiFibration}(L_{n-1}) & \text{ for natural $n \geq 1$ } \\
        L_n &:= \mathrm{SemiTot}(L_{n-1}, l_n, t_n)    & \text{ for natural $n \geq 1$ }
      \end{align*}

@@

      \begin{align*}
        L_{0, 0} &: \mathrm{Semilattice} & \\
        (l_{u, n}, t_{u, n}) &: \mathrm{SemiFibration}(L_{u, n-1}) & \text{for natural $0 \leq u < n_u$, $n \geq 1$ } \\
        L_{u, n} &:= \mathrm{SemiTot}(L_{u, n-1}, l_{u, n}, t_{u, n})    & \text{ for natural $0 \leq u < n_u$, $n \geq 1$ } \\
        L_{u, 0} &:= L_{u-1, \omega} & \text{ for natural $1 \leq u < n_u$ }
      \end{align*}

@@

      To ensure dependency sets don't grow unexpectedly, we require:
      \begin{itemize}
        \item $d_k(t_k(m, m')(v)) \subseteq d_k(v)$.
        \item $d_k(x \vee_{l_k(m)} y) \subseteq d_k(x) \cup d_k(y)$.
      \end{itemize}

>>>>

      The total space $\mathrm{SemiLTot}(L, g)$ is a preorder whose elements consist of pairs $(x, x')$ where $x : L$ and $x' : g(x)$. We consider $(x, x') \leq (y, y')$ when $x \leq y$ and $g(x \leq y)(x') \leq y'$. Consider two elements of the total space, $(x, x'), (y, y')$. Their join is defined as $$(x, x') \vee (y, y') := (x \vee y', g(x \leq x \vee y)(x') \vee g(y \leq x \vee y)(y'))$$.

      \begin{theorem}
        The total space $\mathrm{SemiLTot}(L, g)$ of a semilattice $L$ and a semilattice fibration $g$ is a semilattice.
      \end{theorem}
      \begin{proof}
        We must show that this join is commutative, associative, and idempotent.
        \begin{itemize}
          \item \emph{Commutative}:
            \begin{align*}
              (x, x') \vee (y, y') &= \left(x \vee y, g(x \leq x \vee y)(x') \vee g(y \leq x \vee y)(y')\right) \\
              &= \left(y \vee x, g(y \leq y \vee x)(y') \vee g(x \leq y \vee x)(x')\right) \\
              &= (y, y') \vee (x, x')
            \end{align*}
          \item \emph{Associative}:
            \begin{align*} &((x, x') \vee (y, y')) \vee (z, z')  \\
              =& \left(x \vee y \vee z, g(x \vee y \leq x \vee y \vee z)(g(x \leq x \vee y)(x') \vee g(y \leq x \vee y)(y')) \vee g(z \leq x \vee y \vee z)(z')\right) \\
              =& \left(x \vee y \vee z, g(x \leq x \vee y \vee z)(x') \vee g(y \leq x \vee y \vee z)(y') \vee g(z \leq x \vee y \vee z)(z')\right) \\
              =& \left(x \vee y \vee z, g(x \leq x \vee y \vee z)(x') \vee g(y \vee z \leq x \vee y \vee z)(g(y \leq y \vee z)(y') \vee g(z \leq y \vee z)(z'))\right) \\
              =& (x, x') \vee ((y, y') \vee (z, z'))
            \end{align*}
          \item \emph{Idempotent}: 
            \begin{align*}
              (x, x') \vee (x, x') &= \left(x \vee x, g(x \leq x \vee x)(x') \vee g(x \leq x \vee x)(x')\right) \\
              &= \left(x, g(x \leq x)(x')\right) \\
              &= (x, x')
            \end{align*}
        \end{itemize}
      \end{proof}

@@

      We write $\mathrm{SemiLFibration}(L)$ for the set of semilattice fibrations on $L$.

@@

      The total space $\mathrm{SemiLTot}(L, l, t)$ is then a semilattice whose elements are pairs $(x, x')$ where $x : L$ and $x' : l(x)$. The join is defined as $(x, x') \vee (y, y') := (x \vee y, t(x, x \vee y)(x') \vee t(y, x \vee y)(y'))$. This is equivalent to the above category-theoretic definition, proving it is a semilattice.

@@

      \begin{align*}
        L_0 &: \mathrm{Semilattice} & \\
        (l_n, t_n) &: \mathrm{SemiLFibration}(L_{n-1}) & \text{ for natural $n \geq 1$ } \\
        L_n &:= \mathrm{SemiLTot}(L_{n-1}, l_n, t_n)    & \text{ for natural $n \geq 1$ }
      \end{align*}

@@

      \begin{align*}
        L_{0, 0} &: \mathrm{Semilattice} & \\
        (l_{u, n}, t_{u, n}) &: \mathrm{SemiLFibration}(L_{u, n-1}) & \text{for natural $0 \leq u < n_u$, $n \geq 1$ } \\
        L_{u, n} &:= \mathrm{SemiLTot}(L_{u, n-1}, l_{u, n}, t_{u, n})    & \text{ for natural $0 \leq u < n_u$, $n \geq 1$ } \\
        L_{u, 0} &:= L_{u-1, \omega} & \text{ for natural $1 \leq u < n_u$ }
      \end{align*}

@@

      To ensure dependency sets don't grow unexpectedly, we require:
      \begin{itemize}
        \item $d_k(t_k(m, m')(v)) \subseteq d_k(v)$.
        \item $d_k(x \vee_{l_k(m)} y) \subseteq d_k(x) \cup d_k(y)$.
        \item $d_k(\bot_{l_k(m)}) \subseteq d_k^\star$.
      \end{itemize}
